Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings

### 2015-12-18 manuscript/manuscript_pve.Rmd
delta in colnames of both tables

dust(table1)%>%
  sprinkle_colnames("Volume (L)", 
                        "Seedling mass (g)", 
                        "SLA~TNC-free~ (m^2^ kg^-1^)",
                        "Leaf Starch (%)", 
                        "Leaf Sugars (%)", 
                        "Leaf Nitrogen~TNC-free~ (%)",
                        paste0("Leaf ", greeks['delta'],"^13^C"," (\u2030)")) %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

>>>>

dust(table1)%>%
  sprinkle_colnames("Volume (L)", 
                        "Seedling mass (g)", 
                        "SLA~TNC-free~ (m^2^ kg^-1^)",
                        "Leaf Starch (%)", 
                        "Leaf Sugars (%)", 
                        "Leaf Nitrogen~TNC-free~ (%)",
                        paste0("Leaf ", "$\\delta$","^13^C"," (\u2030)")) %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```
